The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-30 products/manuscript/Manuscript.qmd
Merge remote-tracking branch 'origin/main'

Table 1. Baseline Characteristics of IPTp Trial Participants

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Code that generates HTML widget or output

@@

# Render the table using kableExtra
kbl(
  table_data,
  col.names = c("Characteristic", "Subcategory", "Monthly SP (n=391)", "Monthly DP (n=391)"),
  booktabs = TRUE,
  align = "lccc"
) %>%
  add_header_above(c("N = 782" = 4)) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
  # Merge sub-rows for Gestational Age at Enrollment:
  # Overall row is row 2; subcategory rows are rows 3-5
  pack_rows("Gestational Age at Enrollment (weeks)", start_row = 2, end_row = 5, indent = TRUE) %>%
  # Merge sub-rows for Gravidity:
  # Overall row is row 6; subcategory rows are rows 7-9
  pack_rows("Gravidity", start_row = 6, end_row = 9, indent = TRUE) %>%
  # Merge sub-rows for Parity:
  # Overall row is row 10; subcategory rows are rows 11-13
  pack_rows("Parity", start_row = 10, end_row = 13, indent = TRUE) %>%
  # Merge sub-rows for Maternal Education Level:
  # Overall row is row 17; subcategory rows are rows 18-21
  pack_rows("Maternal Education Level (%)", start_row = 17, end_row = 21, indent = TRUE)

Figure 1: Distribution of Total Malaria Episodes

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Code that generates HTML widget or output

>>>>

Table 1. Baseline Characteristics of IPTp Trial Participants
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Code that generates HTML widget or output

@@

# Render the table using kableExtra
kbl(
  table_data,
  col.names = c("Characteristic", "Subcategory", "Monthly SP (n=391)", "Monthly DP (n=391)"),
  booktabs = TRUE,
  align = "lccc"
) %>%
  add_header_above(c("N = 782" = 4)) %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover")) %>%
  # Merge sub-rows for Gestational Age at Enrollment:
  # Overall row is row 2; subcategory rows are rows 3-5
  pack_rows("Gestational Age at Enrollment (weeks)", start_row = 2, end_row = 5, indent = TRUE) %>%
  # Merge sub-rows for Gravidity:
  # Overall row is row 6; subcategory rows are rows 7-9
  pack_rows("Gravidity", start_row = 6, end_row = 9, indent = TRUE) %>%
  # Merge sub-rows for Parity:
  # Overall row is row 10; subcategory rows are rows 11-13
  pack_rows("Parity", start_row = 10, end_row = 13, indent = TRUE) %>%
  # Merge sub-rows for Maternal Education Level:
  # Overall row is row 17; subcategory rows are rows 18-21
  pack_rows("Maternal Education Level (%)", start_row = 17, end_row = 21, indent = TRUE)
```

Figure 1: Distribution of Total Malaria Episodes
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Code that generates HTML widget or output
